Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
taking comment out and merging git comment into text - hope this is still means what Arfon meant it to

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software, often known as software papers (see \S\ref{sec:software_papers}).
While some journals (e.g., F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals
\cite{aas-sofware-papers}. As the publishers of journals and conveners of domain-specific conferences the authors note the potential importance of professional societies in effecting changes in community practice. \katznote{I can't quite understand what the prev sentence says}

>>>>

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software, often known as software papers (see \S\ref{sec:software_papers}).
While some journals (e.g., F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals
\cite{aas-sofware-papers}. 
Professional societies are in a good position to change their respective communities, as the publishers of journals and conveners of domain-specific conferences; as publishers they can change editorial policies (as AAS has done) and conferences are an opportunity to communicate and discuss these changes with their communities.
